%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------



% Redefine the subsection format


\cvsection{\large Conference Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

%---------------------------------------------------------
\textbf{Oral Presentation}	
%\textbf{\fontsize{10}{17}\selectfont Oral Presentation}

    \begin{itemize}

    \item \textcolor{russell}{Participated in \textbf{The Best Practices in Teaching and Learning Conference} held in May 2023 at Khalifa University, Abu Dhabi, UAE. Organizers: Khalifa University, American University of Sharjah and Amity University Dubai.}
    \item \textcolor{russell}{“Inhomogeneous Microstructure due to Non‑Uniform Solidification Rate in NiTi Triply Periodic Minimal Surface (TPMS) Structures Fabricated via Laser Powder Bed Fusion" presented at \textbf{ASME-International Mechanical Engineering Congress and Exposition (IMECE‑2022)}, Columbus, Ohio, USA in November 2022.}
    \item \textcolor{russell}{“Improvement in shape memory properties of CuAlNiZn shape memory alloys due to addition of grain refiners” presented at \textbf{National Seminar on Advances in Smart \& Functional Materials} held at CSIR-AMPRI, Bhopal between 13-14th January 2017. Organizers: CSIR-AMPRI Bhopal, IIM (Bhopal Chapter), MRSI (Bhopal Chapter) and TSI (Bhopal Chapter).}
     \item \textcolor{russell}{“Study of effect of Fe, Cr and Ti on the martensite phase formation in Cu-12.5wt\%Al-5wt\%Mn SMA” presented at \textbf{International Conference on Materials Science and Technology} held at University of Delhi, Delhi India between 1-4th March 2016. Organizers: International Association of Advanced Materials (IAAM), VBRI Press and University of Delhi.}
    \end{itemize}
    \vspace{-2em} %this is used to give vertical space.
				
\textbf{Poster Presentation}
    \begin{itemize}
    \item \textcolor{russell}{“Microstructural changes and its effect on mechanical as well as shape memory properties in a CuAlNi alloy on addition of dispersoid” presented at \textbf{Recent Innovations in Advanced Materials (RIAM-2018): Physics of Advanced Materials} held at CSIR-AMPRI, Bhopal between 18-19th September, 2018. Organizers: CSIR-AMPRI Bhopal, MRSI (Bhopal chapter), IIM (Bhopal chapter) and MPCOST Bhopal.}
 
     \item \textcolor{russell}{“Changes in properties due to alloying addition of Mn and Cr to Cu-Al-Ni-Zn shape memory alloys” presented at \textbf{India International Science Festival (IISF-2016)} held at CSIR-NPL, New Delhi India between 7-11th December, 2016. Organizers: CSIR-NPL, CSIR-NISCAIR, Ministry of Science \& Technology GOI, Ministry of Earth Sciences GOI, Vigyan Bharti and Vigyan Prasar.}
 
    \item  \textcolor{russell}{“Effect of Addition of Alloying Element Chromium to Cu-Al-Ni-Zn Shape Memory Alloys” presented at \textbf{70th IIM NMD-ATM Conference} held at IIT Kanpur India between 11-13th November 2016. Organizers: IIM, MSE-IIT Kanpur and DMSRDE Kanpur.}
 
    \item \textcolor{russell}{“Role of grain refiners for improved shape memory properties of Cu-12.5wt\%Al-5wt\%Mn Shape Memory Alloy” presented at \textbf{National Seminar on ‘Recent Innovations in Advanced Materials’} held at CSIR-AMPRI, Bhopal India on 29th December, 2015. Organizers: CSIR-AMPRI Bhopal, MRSI (Bhopal Chapter) and MPCOST Bhopal.}
    \end{itemize}
				
\textbf{Conference Publications}
    \begin{itemize}
     \item \textcolor{russell}{\textbf{Shahadat Hussain}, Ali N Alagha, Wael Zaki (2022) Inhomogeneous Microstructure due to Non-Uniform Solidification Rate in NiTi Triply Periodic Minimal Surface (TPMS) Structures Fabricated via Laser Powder Bed Fusion.ASME International Mechanical Engineering Congress and Exposition (IMECE-2022), Ohio, USA.} \newline
     \url{https://doi.org/10.1115/IMECE2022-95320}
 
     \item \textcolor{russell}{\textbf{Shahadat Hussain}, Ashish Kumar Jain, Ansari MA, Abhishek Pandey, Rupa Dasgupta (2017) Study of effect of Fe, Cr and Ti on the martensite phase formation in Cu-12.5wt\%Al-5wt\%Mn SMA. Advanced Materials Proceedings 2(1):22-25.} \url{https://doi.org/10.5185/amp.2017/106}
 
    \end{itemize}
				
\textbf{Book Chapter}			
    \begin{itemize}
    \item \textcolor{russell}{Rupa Dasgupta., Jain A.K., \textbf{Shahadat Hussain}, Abhishek Pandey., V Sampath. (2018) Effect of Alloying Additions on the Properties Affecting Shape Memory Properties of Cu–12.5Al–5Mn Alloy. In: Muruganant M., Chirazi A., Raj B. (eds) Frontiers in Materials Processing, Applications, Research and Technology. Springer, Singapore.} \url{https://doi.org/10.1007/978-981-10-4819-7_33}
    \end{itemize}
\end{cvparagraph}