%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{\large Courses, Training \& Collaborations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}
%---------------------------------------------------------
\begin{itemize}

    \item \textcolor{russell}{\textbf{Our collaboration} involved working alongside Prof. Greg Haidemenopoulos, Director of the Laboratory of Materials in the Department of Mechanical Engineering at the University of Thessaly in Volos, Greece. Together, we focused on \textbf{additive manufacturing using laser bed fusion techniques to create NiTi architected alloys}. Additionally, we conducted microstructural characterizations of these alloys as part of our research efforts.}
    \item \textcolor{russell}{Successfully completed \textbf{10-week teaching certificate course}, conducted by Center for Teaching and Learning (CTL) department at Khalifa University in 2023, covering the modules of effective teaching strategies, assessment techniques, ethics, professionalism and boundaries, educational technology tools, active learning and course alignment, classroom dynamics, intercultural communication, and gender communication styles, with several micro-teaching sessions.}
    \item \textcolor{russell}{Completed \textbf{hydrofluoric acid handling course} in 2021, preparing risk assessment and standard operating procedure forms for chemical etching of 3D printed NiTi samples.}
    \item \textcolor{russell}{Completed \textbf{laboratory training courses} under EHS (Environment, Health and Safety) department at Khalifa University in 2021, covering subjects of introduction to lab safety, compressed gas safety, radiation safety, lab ventilation and fume hood, emergency eye wash station and safety shower, chemical safety and industrial hygiene, handling of cryogenic substance, handling of flammables and combustibles chemicals, lab waste management, administration structure to lab safety and risk assessment, electrical safety, personal protective equipment, emergency preparedness and response, and basic fire safety.}
    \item \textcolor{russell}{Fulfilled the requirements of \textbf{Responsible Conduct of Research (RCR) courses}, conducted by Collaborative Institutional Training Initiative (CITI) Program, Florida, US, in 2020, under Course Learner Group of Engineering and Computing RCR, covering subjects of research involving human subjects, plagiarism,  authorship, collaborative research, conflicts of interest, data management, research misconduct, and introduction to RCR, achieving 100\% grade.}
    \item \textcolor{russell}{During my PhD, I \textbf{trained lab operators} in the casting shop on \textbf{vacuum induction melting and die casting techniques}. Additionally, I created standard operating procedure \textbf{manual} for operating the furnace. I was solely responsible for operating these machines and successfully synthesized Cu-based shape memory alloys from elemental raw materials.}
    \item \textcolor{russell}{Conducted CSIR-800 study on entrepreneurship in a village, involving \textbf{surveying, questionnaire design}, consulting with village head and Patwari, \textbf{data collection, data analysis, data visualization and report creation.}}
    \item \textcolor{russell}{Completed \textbf{14 subjects during PhD coursework} from 2014 to 2016, including materials science and engineering, scientific ethics, technical communications and safety, characterization and analytical techniques, heat treatment, tribology-science and practice, phase transformation, lightweight materials, powder metallurgy, composite science and engineering, nano science and engineering, materials synthesis and processing, computer simulation and design, functional and smart materials, and cellular materials, achieving distinction.}
    \item \textcolor{russell}{I \textbf{partnered} with Prof. Sampath V, a professor in the Department of Metallurgical and Materials Engineering at IIT-Madras, India, to utilize his laboratory for \textbf{synthesizing Cu-based shape memory alloys}. We employed the induction melting technique thereafter, which marked the beginning of the facility in our laboratory at CSIR-AMPRI, Bhopal, India. Furthermore, \textbf{we collaborated on research work and jointly authored research articles} based on our findings.}
\end{itemize}
\end{cvparagraph}