%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{\large Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Division of Engineering, New York University} % Organisation
    {Research Associate} % Job title
    {Abu Dhabi, UAE} % Location
    {Sep 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Hybrid Manufacturing including additive manufacturing via
        stereolithography, fused deposition method, polyjet printing,
        laser powder bed fusion, robotic arm electric arc printing and 
        investment casting.}
        \item {Conducting tensile and fatigue testing, utilizing characterization methods including SEM, XRD, EDS, and metallography, coupled with data analysis and visualization tools like Origin Lab, MS Excel, and various Python libraries.}
        \item {Working on review articles on 3D printing applications in 
        civil engineering sectors.}
        %\item {\textbf{Technical Skills:} EBSD, AFM, Python.}
        %\item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation Skills.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Mechanical Engineering, Khalifa University} % Organisation
    {Postdoctoral Researcher} % Job title
    {Abu Dhabi, UAE} % Location
    {Feb 2020 - Jun 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyzing the attributes of additively manufactured NiTi TPMS structures, such as Schwartz primitive and Schoen gyroid lattices, categorized as porous, cellular, and architected materials.}
        \item {Conducting tensile and fatigue testing, utilizing characterization methods including SEM, XRD, EDS, and metallography, coupled with data analysis and visualization tools like Origin Lab, MS Excel, and various Python libraries.}
        \item {Published 5 research articles in reputed scientific journals and developed lab manuals.}
        %\item {\textbf{Technical Skills:} EBSD, AFM, Python.}
        %\item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation Skills.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CSIR-Advanced Materials and Processes Research Institute} % Organisation
    {Project Fellow} % Job title
    {Bhopal, India} % Location
    {May 2013 - Aug 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Extensive scientific research experience with experimentation, data analysis, teamwork, problem-solving, and effective communication. Proficient in relationship building, negotiation skills.}
        \item {Engaged in diverse experimental tasks: alloy synthesis, metallography, heat treatment, and material characterization using spectroscopy, microscopy, diffractometry, calorimetry, hardness, tensile, and hot rolling.}
        \item {Published 2 research articles, presented research via posters and oral presentations, collaborated with Indian Institute of Technology, Madras.}
        %\item {\textbf{Technical Skills:} Induction Casting, Optical Microscopy, Tensile Testing, Hot Rolling, Heat Treatment}
        %\item {\textbf{Soft Skills:} Communication Skills, Presentation, Scientific Writing, Project Management}
      \end{cvitems}
    }

%---------------------------------------------------------
\begin{comment}
\cventry
    {Department of Mechanical Enginering, Oriental Group of Institutions} % Organisation
    {Lecturer} % Job title
    {Bhopal, India} % Location
    {Sep 2012 - May 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught mechanical engineering subjects, covered materials science, machine component design, mechanics of materials, and basic concepts. Conducted laboratory activities for practical learning.}
        \item {Participated in ISTE workshop on Engineering Thermodynamics, gained skills in classification, problem-solving, and technical presentation.}
        \item {Positive student feedback, completed syllabus on time, promoted academic excellence, supported student improvement, established strong student relationships.}
        \item {\textbf{Technical Skills:} Teaching, Mechanical Engineering, Materials Science}
        \item {\textbf{Soft Skills:} Communication, Presentation, Time Management}
      \end{cvitems}
    }
\end{comment}
%---------------------------------------------------------
\end{cventries}
