\cvsection{\large Expertise}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

\textcolor{russell}{Proficient in operating advanced characterization and analysis equipment:}
\begin{itemize}
    \item \textcolor{russell}{\textbf{Scanning Electron Microscopes (SEM)}: JEOL 7610F, FEI Nova NanovSEM, and FEI Quanta 3D FIB, for imaging and EDS analysis.}
    \item \textcolor{russell}{\textbf{X-ray Diffraction}: Utilized Bruker D2 phasor and Rigaku MiniFlex II for crystal structure analysis.}
    \item \textcolor{russell}{\textbf{Optical Microscopy}: Skilled in using Leica microscopes for detailed observation and analysis.}
    \item \textcolor{russell}{\textbf{Thermal Analysis}: Experienced in performing differential scanning calorimetry using Mettler Toledo DSC 1 and Setaram instruments.}
    \item \textcolor{russell}{\textbf{Optical Emission Spectroscopy}: Proficient in utilizing Bruker Q4 Tasman for elemental analysis of copper and nickel-based alloys.}
    \item \textcolor{russell}{\textbf{Mechanical Testing}: Conducted tensile and compression tests with Instron 5969 static loading and fatigue testing using Instron 8872 machine.}
    \item \textcolor{russell}{\textbf{Metallography}: Skilled in metallographic techniques including grinding, polishing, hot and cold mounting, and ultrasonic and plasma cleaning using Struer and Buehler equipment.}
    \item \textcolor{russell}{\textbf{Chemical Etching}: Competent in performing etching of metal alloys using various etchants, including hydrofluoric acid.}
    \item \textcolor{russell}{\textbf{Casting/Fabrication}: Experience in alloy casting/fabrication using vacuum induction melting furnace.}
    \item\textcolor{russell}{\textbf{Heat Treatment}: Proficient in applying heat treatment processes using muffle furnaces with different temperature profiles and quenching cycles.}
    \item \textcolor{russell}{\textbf{Rolling}: Skilled in both cold and hot rolling techniques of metallic samples using asymmetric two-roll mill machines.}
    \item \textcolor{russell}{\textbf{Additive Manufacturing}: Experienced in the additive manufacturing of NiTi shape memory alloys.}
    \item \textcolor{russell}{\textbf{Software}: Proficient in various software applications including Xpert HighScore Plus, ImageJ, Origin, microscope image analysis software like Gatan Suite, CAD, programming languages such as Python, and word processing tools like LaTeX.}% Skills
\end{itemize}
\end{cvparagraph}